%\input{Praeambel.tex} % Importiere die Einstellungen aus der Präambel
% hier beginnt der eigentliche Inhalt
%\documentclass[14pt]{scrbook}
%\begin{document}
\chapter{Instruments, Functions and Ranges}
\lettrine[lines=2]{\color{blue}\textsf{I}}{}n this chapter, we will introduce all available instruments with their unique options and measurement ranges. It may hopefully provide a useful day to day companion when coding your control file. All the properties with their \texttt{"key"} are accessible via the \texttt{instrument.set("key",value)} or \texttt{instrument.setOptions($\lbrace$"key1":value1, "key2":value2 $\rbrace $} functions.
\section{Keithley 2401}

\textbf{\textsf{Short description}:} Keithley source-measure unit. Is able to source a voltage/current while reading the current/voltage it puts out at the same time. Standard unit in the fishtank lab.\\
\textbf{\textsf{Setter or reader}:} Both\\
\textbf{\textsf{Sourcemode} (\texttt{"sourceMode"}):} Selects the current or voltage sourcemode. Also internally sets the senseMode: The K2401 will measure current when sourcing voltage and vice versa.\\
\textbf{\textsf{Source ranges} (\texttt{"sourceRange"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Voltage:}} [20, 10, 1, 0.1, 0.01, 0.001] V\\
\item \textbf{\textsf{Current:}} [1, 0.1, 0.01, 0.001, \SI{1E-4}, \SI{1E-5}, \SI{1E-6}] A\\
\end{itemize}
\textbf{\textsf{Sense/Measurement ranges} (\texttt{"senseRange"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sensing voltage:}} [21.00, 2.10, 0.21] V\\
\item \textbf{\textsf{Sensing current:}} [\SI{1.05E-4}, \SI{1.05E-5}, \SI{1.05E-6}] A
\end{itemize}
The current sensing ranges go even higher (will be implmented soon), just remember that you might have to increase the compliance if you'd like to increase the sensing range - they are linked (see below in the compliance section)!\\
\textbf{\textsf{Compliance} (\texttt{"compliance"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sensing current:}} [\SI{1.0E-9}, \SI{1.0E-8}, \SI{1.0E-7}] $\rightarrow$ 1.05$\;$A. \\
\item \textbf{\textsf{Sensing voltage:}} [\SI{0.2E-3}, \SI{2E-3}, 0.02] $\rightarrow$ 21$\;$V.\\
\end{itemize}
Note, the "senseRange" limits the lower compliance bounds and thus three values are given each, i.e. [lowerBound1, lowerBound2, etc.] $\rightarrow$ upperBound.\\
\\
\textbf{\textsf{Beep enable} (\texttt{"beepEnable"}):} Boolean. Enables (True) or disables (False) the annoying Keithley beep when an error occurs. Important when debugging.\\
\textbf{\textsf{Output enable} (\texttt{"outputEnable"}}): Boolean. Enables (True) or disables (False) source output. Reading the instrument with output off will result in an error since the instrument is basically off.\\
\textbf{\textsf{Scale factor} (\texttt{"scaleFactor"}}): You can introduce an additional scale factor if you use e.g. a current to voltage amplifier with a known amplification. The instrument will put out the measured value divided by the scale factor. By default, this factor is 1.
\section{Keithley 6517A Electrometer }
\textbf{\textsf{Short description}:} Keithley electrometer/High resistance meter. Able to precisely measure currents down to the few pA range. \\
\textbf{\textsf{Setter or reader}:} Reader only.\\
\textbf{\textsf{Sensemode} (\texttt{"senseMode"}):} Selects the current or voltage sensing mode.\\
\textbf{\textsf{Sense/Measurement ranges} (\texttt{"senseRange"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sensing voltage:}} [2, 20, 200] V\\
\item \textbf{\textsf{Sensing current:}} [\SI{20E-12}, \SI{200E-12}, \SI{2E-9}, \SI{20E-9}, \SI{200E-9}, \SI{2E-6}, \SI{20E-6}, \SI{200E-6}, \SI{2E-3}, \SI{20E-3}] A
\end{itemize}
\textbf{\textsf{Zerocheck} (\texttt{"zeroCheck"}):} Boolean. Enables (True) or disables (False) zerocheck option on the electrometer. Zerocheck basically put a large resistor in line with the measurement line when enabled, thus decreasing the current flow and mitigating possible damage to the sensitive instrument.\\
\textbf{\textsf{Autorange} (\texttt{"autoRange"}):} Boolean. Enables (True) or disables (False) the autorange pyNE function.\\

\section{Yokogawa GS200}
\textbf{\textsf{Short description}:} Power supply known for its low noise. No real measure capabilities. \\
\textbf{\textsf{Setter or reader}:} Setter only.\\
\textbf{\textsf{Sourcemode} (\texttt{"sourceMode"}):} Selects the current or voltage sourcing mode.\\
\textbf{\textsf{Source ranges} (\texttt{"sourceRange"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sourcing voltage:}} [0.01, 0.1, 1, 10, 30] V\\
\item \textbf{\textsf{Sourcing current:}} [0.001, 0.01, 0.1, 0.2] A
\end{itemize}
\textbf{\textsf{Compliance} (\texttt{"compliance"}):}
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sourcing voltage:}} 0.001 $\rightarrow$ 0.1$\;$A\\
\item \textbf{\textsf{Sourcing current/sensing voltage:}} 1 $\rightarrow$ 30$\;$V
\end{itemize}
The YokogawaGS200 only accepts current protection for the 30, 10 and 1$\,$V voltage ranges.\\
\\
\section{SR(S)830 Lock-In Amplifier}
\textbf{\textsf{Short description}:} Wide spread lock-in amplifier with a oscillator frequency of up to ca. 100kHz.\\
\textbf{\textsf{Setter or reader}:} Can act as both.\\
\textbf{\textsf{Time constant} (\texttt{"timeConst"}):} Sets the time constant over which the lock-in integrates.\\
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Possible time constants:}} [\SI{10E-6}, \SI{30E-6}, \SI{100E-6},\SI{300E-6}, \SI{1E-3}, \SI{3E-3}, \SI{10E-3}, \SI{30E-3}, \SI{100E-3},\SI{300E-3},1, 3, 10, 30, 100, 300] seconds.
\end{itemize}
\textbf{\textsf{Sensitivity} (\texttt{"senseRange"}):} Sets the sensitivity of the measurement circuitry.\\
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Sensitivities}:} [\SI{1E-9}, \SI{2E-9}, \SI{5E-9}, \SI{10E-9}, \SI{20E-9}, \SI{50E-9}, \SI{100E-9}, \SI{200E-9}, \SI{500E-9}, \SI{1E-6}, \SI{2E-6}, \SI{5E-6}, \SI{10E-6}, \SI{20E-6}, \SI{50E-6}, \SI{100E-6}, \SI{200E-6}, \SI{500E-6}, \SI{1E-3}, \SI{2E-3}, \SI{5E-3}, \SI{10E-3}, \SI{20E-3}, \SI{50E-3}, \SI{100E-3}, \SI{200E-3}, \SI{500E-3}, 1] V/$\mu$A.
\end{itemize}
Not that the user input always refers to the voltage input, aka the voltage scale is used. The conversion between current and voltage scale is: current scale = voltage scale $\times 10^{-6}$\\
\\
\textbf{\textsf{Input} (\texttt{"input"}):} Sets the input used for the amplifier. In general, the lock in can either measure voltage or current. There are two current inputs with different amplification factors ($10^6$, $10^8$) as well as a normal and a differential ('A-B') voltage measurement.\\
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Available inputs:}} ['A', 'A-B', 'I1', 'I2'].
\end{itemize}
\textbf{\textsf{Frequency} (\texttt{"frequency"}):} Changes the frequency of the sine wave excitation output. Must be in [1, 100 000] Hz.\\
\textbf{\textsf{Amplitude} (\texttt{"amplitude"}):} Changes the amplitude of the sine wave excitation output. Must be in [0.004, 1] V.\\  
\textbf{\textsf{Sweep parameter} (\texttt{"sweepParameter"}):} This option decides which lock-in parameter is swept in case it is used as a \texttt{setter} in a sweep function. This is necessary since there is no 'obvious choice'. So far, it is possible to sweep the excitation frequency or the sine excitation amplitude.\\
\begin{itemize}[noitemsep]
\item \textbf{\textsf{Available parameters}: } ['frequency', 'amplitude'].
\end{itemize}
\textbf{\textsf{Sweep delay} (\texttt{"sweepDelay"}):} Sets the delay between each sweep iteration of aforementioned sweep parameter in seconds. Default is 0.5$\;$s.\\
\textbf{\textsf{Scale factor} (\texttt{"scaleFactor"}}): You can introduce an additional scale factor if you use e.g. a current to voltage amplifier with a known amplification. The instrument will put out the measured value divided by the scale factor. By default, this factor is 1.\\
\textbf{\textsf{Auto sensitivity} (\texttt{"autoSensitivity"}):} Boolean. Enables (True) or disables (False) the autorange pyNE function.\\
